The Astropy Project: Building an open-science project and status of the v2.0 core package

### 2018-03-12 main.tex
Update main.tex
attempt to account for latex in link

\subsection{Coordination of Astropy}
\label{sect:coordcom}
From its inception, \astropy has required coordination to ensure the project
as a whole and its coding efforts are consistent and reasonably efficient.
While many \python projects adopt a ``Benevolent Dictator For Life'' (BDFL)
model\footenote{https://en.wikipedia.org/wiki/Benevolent\_dictator\_for\_life}, \astropy has instead opted for a \emph{coordination committee}.  This
is in part due to the nature of the project as a large-scale collaboration
between many contributors with many interests, and in part due to simply the
amount of work that needs to get done.  For the latter reason, the
project has expanded the committee from three to four members starting in
2016.

@@

\begin{deluxetable*}{cccp{3in}c}
  \tablecaption{Registry of provisionally accepted affiliated packages.}
  \label{tab:registry_prov}
    \tablehead{
        \colhead{Package Name} &
        \colhead{Stable} &
        \colhead{PyPI Name} &
        \colhead{Maintainer} &
        \colhead{Citation}
      }
    \startdata
      \input{registry_prov.tex}
    \enddata
\end{deluxetable*}

>>>>

\subsection{Coordination of Astropy}
\label{sect:coordcom}
From its inception, \astropy has required coordination to ensure the project
as a whole and its coding efforts are consistent and reasonably efficient.
While many \python projects adopt a ``Benevolent Dictator For Life'' (BDFL)
model, \astropy has instead opted for a \emph{coordination committee}.  This
is in part due to the nature of the project as a large-scale collaboration
between many contributors with many interests, and in part due to simply the
amount of work that needs to get done.  For the latter reason, the
project has expanded the committee from three to four members starting in
2016.

@@
